Virtualisierung eines Echtzeit-Betriebssystems zur Steuerung eines Roboters mit Schwerpunkt auf die Einhaltung der Echtzeit

### 2024-04-16 Masterarbeit_Robotik_Pamuk.tex
Updated analyze_trace.py to include PID

@@

@@

\begin{table}[H]
	\centering
	\caption[Kernel and Patches]{Kernel and Patches}
	\label{tab:kernel_configuration}
	\begin{tabular}{|c|c|}
		\hline
		\textbf{Kernel} & \textbf{Patches} \\ \hline
		.               & .                \\ \hline
		.               & .                \\ \hline
	\end{tabular}
\end{table}

@@

\clearpage
\section{Interrupt Requests Handling}\label{sec:irq_handling}
Once the CPUs were isolated, Interrupt Requests Handling was the next step. Interrupt Requests are used to send a signal to the CPU, prompting it to 'interrupt' its current task and divert its attention to another task. This allows hardware devices to communicate with the CPU through frequent context switches, which can lead to performance degradation, especially in high-performance computing or real-time scenarios. To mitigate this, the IRQs needed to be removed from the isolated CPUs. This was done by manipulating a file in the proc filesystem, namely \texttt{/proc/irq/default\_smp\_affinity}. The value in the \texttt{smp\_affinity} file is a bitmask in hexadecimal format. Each bit in this mask corresponds to a CPU in the system. The least significant bit (LSB) on the right corresponds to the first CPU (CPU0), and the significance increases towards the left until CPU19. In a system with 20 CPUs, if every CPU was reserved for one IRQ, the value for \texttt{smp\_affinity} would be FFFFF. The script in code \ref{script:smp_affinity} was written to check and log the distribution of Interrupt Requests across each CPU in Salamander 4.

@@

By changing the values in

, I could effectively control the assignment of IRQs, ensuring they would not be handled by the isolated CPUs. This manipulation was done carefully, considering the implications and ensuring the stability and integrity of the system.

Through this approach, I was able to create a more streamlined and efficient environment for the execution of specific tasks on the isolated CPUs. By reducing the interruptions caused by IRQs, the isolated CPUs were able to focus more on their assigned tasks, potentially leading to improved performance and more predictable execution times.

>>>>

\begin{table}[h!]
	\centering
	\begin{minipage}{.5\textwidth}
	\centering
	\caption{Host report (Total of 445.908)}
	\label{tab:results_host_report}
	\begin{tabular}{|c|c|c|}
	\hline
	PID & Task & Count \\ \hline
	182579 & qemu-system-x86 & 302.748 \\ \hline
	0 & \textless{}idle\textgreater{} & 112.911 \\ \hline
	182618 & vhost & 21.204 \\ \hline
	182572 & qemu-system-x86 & 7.597 \\ \hline
	182755 & qemu-system-x86 & 644 \\ \hline
	182754 & qemu-system-x86 & 643 \\ \hline
	181870 & kworker/19:1 & 139 \\ \hline
	3820 & kworker/19:1H & 16 \\ \hline
	94 & migration/19 & 6 \\ \hline
	\end{tabular}
	\end{minipage}%
	\begin{minipage}{.5\textwidth}
	\centering
	\caption{Guest report (Total of 362.370)}
	\label{tab:results_guest_report}
	\begin{tabular}{|c|c|c|}
	\hline
	PID & Task & Count \\ \hline
	0 & \textless{}idle\textgreater{} & 150.744 \\ \hline
	331 & LRT-Main & 56.697 \\ \hline
	377 & trace-cmd & 48.507 \\ \hline
	346 & CLI & 26.426 \\ \hline
	378 & kthreadd & 25.837 \\ \hline
	340 & MainTaskLow & 19.291 \\ \hline
	339 & \textless{}...\textgreater{} & 9.980 \\ \hline
	34 & MainTaskHigh & 9.185 \\ \hline
	327 & LE-Logger & 4.965 \\ \hline
	369 & kworker/0:0 & 2.793 \\ \hline
	321 & kWorker-LRT & 2.542 \\ \hline
	328 & LRTMgr-Main & 1.651 \\ \hline
	34 & LrtMgrCyclic & 1.220 \\ \hline
	332 & cobalt\_printf & 1.112 \\ \hline
	325 & LE-System & 534 \\ \hline
	343 & TCP-Listen & 187 \\ \hline
	15 & rcu\_preempt & 162 \\ \hline
	25 & kcompactd0 & 122 \\ \hline
	58 & kworker/0:1H & 96 \\ \hline
	63 & kworker/u2:2 & 89 \\ \hline
	8 & jbd2/sda-8 & 86 \\ \hline
	22 & kworker/0:1 & 56 \\ \hline
	1 & init & 31 \\ \hline
	2 & kthreadd & 25 \\ \hline
	375 & trace-cmd & 24 \\ \hline
	14 & ksoftirqd/0 & 8 \\ \hline
	\end{tabular}
	\end{minipage}
	\end{table}

@@

\subsection{Generic Ubuntu}

\subsection{Real-Time Ubuntu}

@@

@@

\clearpage
\section{Interrupt Requests Handling}\label{sec:irq_handling}
Once the CPUs were isolated, Interrupt Requests Handling was the next step. Interrupt Requests are used to send a signal to the CPU, prompting it to 'interrupt' its current task and divert its attention to another task. This allows hardware devices to communicate with the CPU through frequent context switches, which can lead to performance degradation, especially in high-performance computing or real-time scenarios. To mitigate this, the IRQs needed to be removed from the isolated CPUs. This was done by manipulating a file in the proc filesystem, namely \texttt{/proc/irq/<IRQ>/smp\_affinity}. The value in the \texttt{smp\_affinity} file is a bitmask in hexadecimal format. Each bit in this mask corresponds to a CPU in the system. The least significant bit (LSB) on the right corresponds to the first CPU (CPU0), and the significance increases towards the left until CPU19. In a system with 20 CPUs, if every CPU was reserved for one IRQ, the value for \texttt{smp\_affinity} would be FFFFF. The script in code \ref{script:smp_affinity} was written to check and log the distribution of Interrupt Requests across each CPU in Salamander 4.

@@

\noindent By changing the values of the \texttt{smp\_affinity} files of the respective IRQs, the assignment of IRQs was controlled so that they would not be handled by the isolated CPU. This reduced the interruptions caused by IRQs and the isolated CPUs were able to focus more on their assigned tasks.
